Variational Monte Carlo on Bosonic Systems

### 2018-04-06 project_1/article/article.tex
Spell check figure

        % Flow chart for description of automatic blocking algorithm
        \begin{figure}
            \centering
            % Defining blocks of flowchart
            \tikzstyle{decision} = [diamond, draw, fill=blue!20,
                text width=5em, text badly centered, node distance=3cm, inner sep=0pt]
            \tikzstyle{block} = [rectangle, draw, fill=blue!20,
                    text width=11em, text centered, rounded corners, minimum height=4em]
            \tikzstyle{line} = [draw, -latex']

@@

                % Nodes
                \node [block] (init) {Start with $\mathbf{X}_i$, $i=0$};
                \node [block, below of=init] (variance) {Compute variance and autocovariance of $\mathbf{X}_i$, $s_i$ and $\gamma_i$};
                \node [block, below of=variance] (transform)
                    {Transform data $(\mathbf{X}_{i+1})_k = \frac{1}{2}\left((\mathbf{X})_i)_{2k-1} + (\mathbf{X}_i)_{2k} \right)$};
                \node [block, right=1.0cm of transform] (i+1) {Next iteration: $i = i + 1$.} ;
                \node [decision, below of = transform] (x_size) {Length of $\mathbf{X}_{i + 1} \geq 2$ ? };
                \node [block, below of=x_size] (m_test) {Compute test statistic $M_j$ from $s_j$ and $\gamma_j$ for all $j$.};
                \node [block, below of=m_test] (magic_numbers) {Find first $k$ so that $M_k \leq q_{d-k}(1-\alpha)$};
                \node [block, below of=magic_numbers] (return) {Return $s_k^2/n_k$};

                % Edges
                \path [line] (init) -- (variance);
                \path [line] (variance) -- (transform);
                \path [line] (transform) -- (x_size);
                    \path [line] (x_size) -| node [near start] {yes} (i+1);
                    \path [line] (i+1) |- (variance);
                \path [line] (x_size) -- node [near start] {no} (m_test);
                \path [line] (m_test) -- (magic_numbers);
                \path [line] (magic_numbers) -- (return);
            \end{tikzpicture}
            \caption{Flow chart depicting the automatic blocking method for finding a better estimate for sample variance.}
            \label{fig:blocking}
        \end{figure}

>>>>

            % Flow chart for description of automatic blocking algorithm
            \begin{figure}
                \centering
                % Defining blocks of flowchart
                \tikzstyle{decision} = [diamond, draw, fill=blue!20, text
                width=5em, text badly centered, node distance=3cm, inner
                sep=0pt]

                \tikzstyle{block} = [rectangle, draw, fill=blue!20, text
                width=11em, text centered, rounded corners, minimum height=4em]

                \tikzstyle{line} = [draw, -latex']

@@

                    % Nodes
                    \node [block] (init) {Start with $\mathbf{X}_i$, $i=0$};

                    \node [block, below of=init] (variance) {Compute variance
                    and autocovariance of $\mathbf{X}_i$, $\sigma_i$ and
                    $\gamma_i$};

                    \node [block, below of=variance] (transform) {Transform data
                    $(\mathbf{X}_{i+1})_k =
                    \frac{1}{2}\left((\mathbf{X})_i)_{2k-1} +
                    (\mathbf{X}_i)_{2k} \right)$};

                    \node [block, right=1.0cm of transform] (i+1) {Next
                    iteration: $i = i + 1$.} ;

                    \node [decision, below of = transform] (x_size) {Length of
                    $\mathbf{X}_{i + 1} \geq 2$ ? };

                    \node [block, below of=x_size] (m_test) {Compute test
                    statistic $M_j$ from $\sigma_j$ and $\gamma_j$ for all
                    $j$.};

                    \node [block, below of=m_test] (magic_numbers) {Find first
                    $k$ such that $M_k \leq q_{d-k}(1-\alpha)$};

                    \node [block, below of=magic_numbers] (return) {Return
                    $\sigma_k^2/n_k$};

                    % Edges
                    \path [line] (init) -- (variance);
                    \path [line] (variance) -- (transform);
                    \path [line] (transform) -- (x_size);
                        \path [line] (x_size) -| node [near start] {yes} (i+1);
                        \path [line] (i+1) |- (variance);
                    \path [line] (x_size) -- node [near start] {no} (m_test);
                    \path [line] (m_test) -- (magic_numbers);
                    \path [line] (magic_numbers) -- (return);
                \end{tikzpicture}
                \caption{Flow chart depicting the automatic blocking method for
                finding a better estimate for the sample variance.}
                \label{fig:blocking}
            \end{figure}
